On the Dynamics of Anthropomorphism in Robotics \thanks{This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.}

### 2013-05-21 anthropomorphism.tex
new figure and new text multi-layered anthropomorphism

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\graphicspath{{figs/}}
\usepackage{tikz}
\usetikzlibrary{shapes}
%
\usepackage{amsmath} 
\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
\usepackage{color, soul}
\usepackage{url}
\usepackage[numbers, square, comma, sort&compress]{natbib}
\usepackage{multirow}
\usepackage{array}

@@

	Literature on anthropomorphism (in robotics) is quite diverse and one strives hard to extract a coherent conclusion. There is no commonly accepted definition about the terms used and the terminology is not clear. However the terms \textit{anthropomorphic or human-like are often used as if their meanings are clear and agreed upon"} \cite{persson_anthropomorphism_2000}. Consequently, Duffy \cite{duffy_anthropomorphism_2002} argues that terms might even be misused. For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, however, others argue that anthropomorphism emerges in the \textit{interaction} between the technology and the user, thus a system or an artifact does not "contain anthropomorphism" \textit{per se} \cite{persson_anthropomorphism_2000}. Further, robotics is a multi-disciplinary field and researchers from very different domains might have diverse or even contradictory understandings of anthropomorphism. Epley \textit{et al.} \cite{epley_seeing_2007} notice that despite the fact that anthropomorphism in the perception of non-human agents is commonly observed, it is poorly understood. The phenomenon itself has been found to be very complex but sometimes subtle and hard to study. Another constraint that limits the reliability of some findings is, that most experiments on anthropomorphism are conducted in controlled lab-settings during short-term interactions. This experimental setting (short term and laboratory context) can be critical when studying a social phenomenon like anthropomorphism and possibly lead to over-interpretations. Some studies also seem to contrast two or more different anthropomorphic and mechanical systems that might not be appropriate for comparison under the given context and research question. \hl{say more}

@@

@@

	Initially, there is a given potential that a robot will be anthropomorphized. Our proposed function of anthropomorphism starts with this what we call \textit{initial capital} of anthropomorphism (ICA) at time point = 0, which describes the first (imagined) contact to the robot. This time point can temporally be before the first real physical interaction with the robot, for instance, when a person learns about the existence of vacuum-cleaning robots (\textit{e.g.} when one sees an advertisement of the robot, or discusses about it with a friend). In this phase of "pre-interaction", people form initial expectations toward the robot and imagine how they will use / interact with it, before they actually start interacting with it in real. Therefore, the time point = 0 can be understood as user experience = 0. \hl{[pre-adoption, rogers]} How can we hypothetically quantify the ICA? We argue, that the potential to anthropomorphize a robot is mainly determined by three factors, which we would like to introduce as the "Three P's":

@@

	The ICA builds the sum of some hypothetical values for the "Three P's" and ranges between the theoretical values of 0 and 1.
	For \textbf{personality}, we suggest to apply Epley \textit{et al.}'s psychological \textit{"Three Factory Theory"} of anthropomorphism. For instance, children generally tend to anthropomorphize objects more than adults. Also, a person who lacks social connection is said to be more likely to anthropomorphize. Both aspects would increase the ICA.
	For \textbf{perception}, we understand that a robot that follows an anthropomorphic design (e.g. NAO) leads to a higher ICA than a rather functional robot (e.g. Roomba). Also, a robot that displays facial expressions would increase the ICA. However, \hl{as discussed before} a classification of the "amount" of anthropomorphic design in a robot, as for instance suggested by Fong \textit{et al.} \cite{fong_survey_2003}, can be difficult.
	For \textbf{purpose}, we propose that the real or imagined context in which a robot is used, impacts how far the robot will be attributed human-social characteristics. We	draw on findings such as presented in Joosse \textit{et al.}. The authors showed that when the same robot (NAO) is used in a different task context (cleaning task \textit{vs.} tour guide), this influences the perception of the "personality" of the robot. In general, we think that a robot which is (imagined to be) used in a social, entertaining or playful context leads to a higher ICA than a robot which is used for a serious task (security, rescue, etc.). This idea receives support from \hl{XX (Kiesler / Goetz?)} work that revealed that people prefer a serious robot for serious tasks and a less serious robot for more playful tasks \hl{REF}. Also, we suggest that the environmental context in which people experience and interact with the robot impacts the ICA. When several people who might be friends interact simultaneously with the robot this might lead to an increased ICA \hl{study: people are more emotional when watching TV in company than when watching TV on their own}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\graphicspath{{figs/}}
\usepackage{tikz}
\usetikzlibrary{shapes}
%
\usepackage{amsmath} 
\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
\usepackage{color, soul}
\usepackage{url}
\usepackage[numbers, square, comma, sort&compress]{natbib}
\usepackage{multirow}
\usepackage{array}
\usepackage{fixltx2e}
\usepackage{textcomp}

@@

	Literature on anthropomorphism (in robotics) is quite diverse and one strives hard to extract a coherent conclusion. There is no commonly accepted definition about the terms used and the terminology is not clear. However the terms \textit{anthropomorphic or human-like are often used as if their meanings are clear and agreed upon"} \cite{persson_anthropomorphism_2000}. Consequently, Duffy \cite{duffy_anthropomorphism_2002} argues that terms might even be misused. For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, however, others argue that anthropomorphism emerges in the \textit{interaction} between the technology and the user, thus a system or an artifact does not "contain anthropomorphism" \textit{per se} \cite{persson_anthropomorphism_2000} but only gives rise to the process of anthropomorphizing in a given user and situation. Further, robotics is a multi-disciplinary field and researchers from very different domains might have diverse or even contradictory understandings of anthropomorphism. Epley \textit{et al.} \cite{epley_seeing_2007} notice that despite the fact that anthropomorphism in the perception of non-human agents is commonly observed, it is poorly understood. The phenomenon itself has been found to be very complex but sometimes subtle and hard to study. Another constraint that limits the reliability of some findings is, that most experiments on anthropomorphism are conducted in controlled lab-settings during short-term interactions. This experimental setting (short term and laboratory context) can be critical when studying a social phenomenon like anthropomorphism and possibly lead to over-interpretations. Some studies also seem to contrast two or more different anthropomorphic and mechanical systems that might not be appropriate for comparison under the given context and research question. \hl{say more}

@@

\subsection{Anthropomorphism as a multi-layered phenomenon}
\label{sec:3.4}

Anthropomorphism can also be viewed as an \textit{experience} that arises in the \textit{interaction} between a set of user expectations and external reality \cite{persson_anthropomorphism_2000}, (see Figure)

an \textit{understanding} of complex -- not necessarily human -- patterns of behavior in the world, in order to make sense of it: \textit{"Anthropomorphism is a way of simplifying and thereby making sense of the environment by projecting a host of expectations about human life onto aspects of that environment."} \cite{persson_anthropomorphism_2000}
Persson \textit{et al.} explored anthropomorphism triggered by computer interfaces and system and we believe their perspective on anthropomorphism could also be applied in HRI. The authors suggest that the social phenomenon is not only one single process but that it involves several levels, \textit{e.g.} primitive psychology, folk-psychology, social stereotypes, and emotional anthropomorphism. We would like to take up the proposition to discriminate different levels of anthropomorphism, since each has its own characteristics and involves specific types of user expectations. This differentiation could allow to draw inferences on the human-robot relationship from the observed level of anthropomorphism.

\begin{figure}\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.42]{persson_anthropomorphism.png}
% figure caption is below the figure
 \caption{Anthropomorphism emerges in the (real or imagined) interaction between robot and user; illustration taken from \cite{persson_anthropomorphism_2000} \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
 \label{fig:2}       % Give a unique label
 \end{figure}

@@

	Initially, there is a given potential that a robot will be anthropomorphized. Our proposed function to model the dynamics of anthropomorphism starts with this what we call \textit{initial capital of anthropomorphism} (ICA) at time point $t_{0}$, which describes the first (real or imagined) contact to the robot (see Figure \ref{fig:dynamics}). Time point $t_{0}$ can temporally be before the first real physical interaction with the robot, for instance, when a person learns about the existence of vacuum-cleaning robots and imagines using one (\textit{e.g.} when one watches an advertisement of the robot, or observes one at a trade show). In this stage of "pre-interaction", people form initial expectations toward the robot and imagine how they will use / interact with it. Time point $t_{0}$ can be understood as duration of interaction = 0 and user experience = 0. How can we hypothetically quantify the ICA on a normalized scale of anthropomorphism? For this, we suggest, what we call the \textit{"Three P's"}. These are three main factors that \textit{a priori} determine the potential to anthropomorphize a robot:

@@

	The ICA comprises some hypothetical values for each of the \textit{"Three P's"}, such that different ICA values can be obtained, given the robot, human user, and environmental context.
	For \textbf{personality}, we suggest to apply Epley \textit{et al.}'s psychological \textit{"Three Factory Theory"} of anthropomorphism. For instance, children generally tend to anthropomorphize objects more than adults. Also, a person who lacks social connection is said to be more likely to anthropomorphize. Both aspects would increase the ICA. This means that, one and the same robot used in a different context or by a different user, can lead to a different ICA.

	For \textbf{perception}, we understand that a robot that follows an anthropomorphic design (e.g. NAO) leads to a higher ICA than a rather functional robot (e.g. Roomba). Also, a robot that displays facial expressions would increase the ICA. However, \hl{as discussed before} a classification of the "amount" of anthropomorphic design in a robot, as for instance suggested by Fong \textit{et al.} \cite{fong_survey_2003}, can be difficult.

	For \textbf{purpose}, we propose that the real or imagined context in which a robot is used, impacts how far the robot will be attributed human-social characteristics. We	draw on findings such as presented in Joosse \textit{et al.}. The authors showed that when the same robot (NAO) is used in a different task context (cleaning task \textit{vs.} tour guide), this influences the perception of the "personality" of the robot. In general, we think that a robot which is (imagined to be) used in a social, entertaining or playful context leads to a higher ICA than a robot which is used for a serious task (security, rescue, etc.). This idea receives support from \hl{XX (Kiesler / Goetz?)} work that revealed that people prefer a serious robot for serious tasks and a less serious robot for more playful tasks \hl{REF}. Also, we suggest that the environmental context in which people experience and interact with the robot impacts the ICA. When several people who might be friends interact simultaneously with the robot this might lead to an increased ICA \hl{study: people are more emotional when watching TV in company than when watching TV on their own}.

\subsection{Anthropomorphism during Initialization Phase}
\label{sec:7.2}

(\textit{INITIALIZATION})

\subsection{Anthropomorphism during Familiarization Phase}
\label{sec:7.3}

\subsection{Anthropomorphism during Stabilization Phase}
\label{sec:7.4}
